---
title: "Teste T"
author: "Douglas Vinícius"
date: "10 de junho de 2019"
output: 
  ioslides_presentation:
     widescreen: true
     smaller: true
     transition: slower
     logo: 
     
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Teste de Hipóteses?

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

http://www.portalaction.com.br/inferencia/462-2o-caso-variancias-desconhecidas-porem-iguais


An Introduction to Statistical Inference and Its Applications with R

http://www.sthda.com/english/wiki/unpaired-two-samples-t-test-in-r

http://www.sthda.com/english/wiki/unpaired-two-samples-t-test-in-r

https://www.statmethods.net/stats/ttest.html

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

